

\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Saurabh}{Singh}{ %| \href{http://fb.co/dd}{fb.co/dd}\\%
\href{mailto:saurabhsunilsingh@gmail.com}{saurabhsunilsingh@gmail.com} | +91-8603652060 | \href{mailto:singh.sunil@student.amity.edu}{singh.sunil@student.amity.edu}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 



\subsection{Amity University}
\descript{B.Tech in Computer Science}
\location{Dec 2020 | Noida, IN}
Amity School of Engineering \& Technology\\
\location{ CGPA: 7.19 / 10.0 }
\sectionsep

\subsection{B.S.College}
\descript{12th }
\location{Grad. April 2015 | Patna, IN}
\sectionsep

\subsection{Free Methodist School}
\descript{10th}
\location{Grad. April 2013|  Yavatmal, IN}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Facebook:// \href{https://www.facebook.com/saurabhsunilsingh/}{\bf Saurabh Singh} \\
Github:// \href{https://github.com/saurabhsunilsingh}{\bf Saurabh Singh} \\
LinkedIn://  \href{https://www.linkedin.com/in/saurabhsunilsingh/}{\bf saurabhsunilsingh} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
 Java\\
 C\\
 C++\\
 Python\\
Software Engineering \\
Advanced Java\\
DBMS\\
Operating Systems \\
Artificial Intelligence + M.L. \\
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Java \textbullet{} Unqork  \\
\location{Over 1000 lines:}
Python \textbullet{} CSS \textbullet{} HTML \\
\location{Familiar:}
C \textbullet{} C++ \textbullet{} Sql
\sectionsep
\subsection{Dev Tools}
\location{Unqork:}
\textbullet{}Professional Configurator \\
\textbullet{}Associate Configurator\\ 
\textbullet{}Novice Badge  \\
\location{Majesco:}
\textbullet{}Digital 1st Configurator
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{KPMG}
\descript{| Associate Consultant }
\location{Dec 2020 - Present | Banglore, IN}
\vspace{\topsep}
\begin{tightemize}
\item Senior Config Specialist - Unqork
\end{tightemize}
\sectionsep

\runsubsection{Kyrion Technologies}
\descript{| Machine Learning Intern }
\location{May 2019 – June 2019 | Noida, IN}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item 30 students were selected out of 1200.
\item Implemented \& learnt machine learning algorithms. 
\item Contributed by Data Cleansing in a team project. 
\end{tightemize}
\sectionsep

\runsubsection{HP Enterprise}
\descript{| Artificial Intelligence Intern }
\location{June 2019 – June 2019 | Noida, IN}
\begin{tightemize}
\item Worked on the Twitter Dataset and created a Sentimental Analysis Model
\item Cleared the HPE Skill Assessment.
\item Implemented A.I. Algorithms on Dataset from Kaggle 
\end{tightemize}
\sectionsep

\runsubsection{JIO}
\descript{| Support Intern}
\location{June 2018 – Jul 2018 | Patna, IN}
\begin{tightemize}
\item Conducted Data Collection Drives for Local SMEs. 
\item Worked on documentation of the Data Collected.
\item Led a team for Accurate data collection and submission on Microsoft Kaizala App to Jio Analysts .
\item Gold Certificate with a Top 500 national rank. 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Transamerica}
\descript{| Senior Config Specialist}
\location{June 2023 - Present | Bangalore, IN}
Working on Insurance Portal, fixing issue and defects raised and adding features and completing requirements regarding module development.
\sectionsep

\runsubsection{Broadridge}
\descript{| Senior Config Specialist}
\location{Sep 2022 - June 2023 | Bangalore, IN}
Worked on client onboarding portal and bug solving for financial service provider, serving UBS Bank. Using a Low-Code No-Code Tool Unqork assisted the Lead developer,in module construction using the wireframe, business rules and specifications provided. Multiple modules were tested and deployed to production. Majorly working on multiple bug fixes and issues encountered helping out colleagues with defects and contributing to the team goal as whole.
\sectionsep

\runsubsection{First Manhattan Co.}
\descript{| Senior Config Specialist}
\location{Jan 2022 – Sep 2022 | Bangalore, IN}
Worked with KPMG on a American Advisory Firm client onboarding portal.  Also worked on Module development and PDF generation, Transforms and Webpage designing using Unqork. Furthermore contributed to development process through Bug fixing, error correction and development documentation.
\sectionsep

\runsubsection{Manulife}
\descript{| Junior Config Specialist}
\location{April 2021 – Dec 2021 | Bangalore, IN}
Worked with KPMG on a Canadian Insurance provider client to completely revamp the current insurance application software using Unqork. Was assigned task to created modules of given specifications and design wireframes. Also did Bug fixes and Data mapping for Document Generation.
\sectionsep

\runsubsection{Cisco}
\descript{| Novice Config }
\location{April 2021 – Dec 2021 | Bangalore, IN}
Worked with KPMG for a Technology Corporation to conduct test on modules and write documents of the development workflow.
\sectionsep
\end{minipage}



 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.33\textwidth}
\section{Awards} 
\begin{tabular}{rll}
2021	     & top 50  &Kudos- Performer\\
2022	     & 1\textsuperscript{st}/50  & SuperTeam- Low Code No Code\\
2020         & 8\textsuperscript{th}/120  & Coding Blocks- Java Crux\\
2018        & Silver  & Sanghatan Hockey Tournament\\
2019         & Bronze  & Sanghatan Hockey Tournament

\end{tabular}

\sectionsep

\end{minipage}

 
\end{document}  \documentclass[]{article}
